Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-12-01 cbm-rbd-paper.tex
sdf comments sec 1

\begin{abstract}
We propose a new way of developing a condition-based maintenance policy for complex systems,
based not on a one-dimensional continuous degradation signal,
but on the status of all components within a system.

By means of the survival signature,
a generalization of the system signature allowing for multiple component types,
we obtain a predictive distribution for system survival time
%(also known as RUL, remaining useful life)
(known as residual life distribution, RLD)
based on which of the system's components currently function or not,
and the current age of the functioning components.

Component time to failure is modeled by a Weibull distribution with fixed shape parameter.
The scale parameter is iteratively updated in a Bayesian fashion
using the current (censored and non-censored) component lifetimes.
Each component type has a separate model that may also include test data.

The cost-optimal moment of repair for the system is obtained by minimizing the one-cycle unit cost rate.
The unit cost rate is recalculated at fixed time points,
leading to a dynamic policy since the aging of components and possible failures will change the cost-optimal moment of repair.
\end{abstract}

\begin{keyword}
condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep one-cycle unit cost rate\end{keyword}
\end{frontmatter}

@@

***main message:
can do CBM for systems without degradation signal,
especially useful for redundant systems,
dynamic policy using one-cycle unit cost rate (exact, unlike renewal theorem based!),
using iterative Bayesian update of component models,
thus taking all information into account (history and current status)

***Bayesian approach allows component models to include expert info, test data (if available),
and information that can be gained from the behaviour of components in the running system
in the form of censored and non-censored component lifetimes

***we argue that our approach is CBM because it takes current system state into account
and adjusts the moment of maintenance accordingly.

\subsection*{---------------------}
***general discussion on CBM as usual

@@

***In both cases, maintenance decision via control limit / threshold for the signal
(RUL not explicitely calculated)
by minimizing the expected unit cost rate,
which is often approximated using the renewal reward theorem.
%but in practice threshold often not known

\subsection*{---------------------}

@@

***compare to $M^*$ out of $N$ policy:
we are dynamic (would mean for a $M^*$ out of $N$ policy that $M^*$ decreases over time due to component aging),
we learn about component lifetimes,
and we allow for set-up time

\section{Literature***}

>>>>

\begin{abstract}
We propose a new condition-based maintenance policy for complex systems,
based on the status (working, defective) of all components within a system,
as well as the relaibility block diagaram of the system.

By means of the survival signature,
a generalization of the system signature allowing for multiple component types,
we obtain a predictive distribution for the system survival time
%(also known as RUL, remaining useful life)
(also known as residual life distribution, RLD)
based on which of the system's components currently function or not,
and the current age of the functioning components.

The time to failure of the components of the system
is modeled by a Weibull distribution with a fixed shape parameter.
The scale parameter is iteratively updated in a Bayesian fashion
using the current (censored and non-censored) component lifetimes.
Each component type has a separate (Weibull) model that may also include test data.

The cost-optimal moment of replacement for the system is obtained by minimizing
the expected cost rate per unit of time.
The unit cost rate is recalculated when components fail
or at the end of every (very short) fixed inter-inspection interval,
leading to a dynamic maintenance policy,
since the aging of components and possible failures will change the cost-optimal moment of repair in the course of time.
Via numerical experiments, some insight into the performance of the policy is given.
\end{abstract}

\begin{keyword}
condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep unit time cost rate\end{keyword}
\end{frontmatter}

@@

Both in practice and academics,
there is a growing interest in CBM (condition-based maintenance), see e.g.,
\citet[pp.~15--55]{2016:oldekeizer}
The central idea behind CBM is to maintain systems or components at the right time,
i.e., before they fail, but not too early, in order to keep their reliability high and operating costs low.
In this context a trade-off is made between the risk of failure during operation
(which can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
and the costs of premature maintenance (wasting potential component or system lifetime,
downtime cost, cost of executing unnecessary maintenance activities).

Among the reasons for the above interest are the importance of increasingly short and
reliable delivery times, and decreasing profit margins due to worldwide competition.
All kinds of technical improvements have made it possible % it is more / better / earlier possible
to estimate the condition of systems as a whole as well as their undelying components,
whereas the cost for these technologies is decreasing rapidly,
making the use of CBM policies even more feasible.

Most CBM policies are based on a directly observable, continuously measurable condition or degradation signal.
Alternatively, such a signal or health status is constructed
using indirect measurements to determine the remaining useful life or time to failure of a system,
see, e.g., \citet{2014:rul-review, 2011:rul-review-statistical}.

In this paper, we propose an inspection-based CBM policy
for when no degradation signal for the system is available,
but where the status (working or not working) of the components can be monitored continuously.
In this situation, one can use the system's reliability block diagram
and information with respect to the status of its components
to directly calculate the system residual life distribution (RLD),
and base the maintenance policy for the system on this distribution.
(In fact, our CBM policy can be seen as based on a multivariate degradation signal,
where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.)

There are 3 types of triggers to review the system in our new policy:
at the end of each very short inspection interval (1),
directly after the failure of a component where the system still functions (2),
and directly after the failure of a component due to which the system as a whole no longer can function (3).

In case of a trigger of type (1),
the currently used model for system failure times is updated
to account for the aging of components,
and the extra lifetime observed for the components.
The latter information is taken into account via right-censored observations
in a Bayesian parameter update step.

In case of a trigger of type (2),
when a component has failed since the last inspection but the system is still functioning,
also the reliability block diagram of the system is updated.
Based on the above changes,
it is determined in both cases whether the system should be replaced now,
or that this decision should be postponed until the next planned inspection moment,
accepting the risk of a system breakdown before.
In this context, the optimal moment of maintenance
is calculated based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle,
where an operational cycle starts with a new system, and ends after this system has been replaced by a(n as good as) new system.

In case of a trigger of type (3),
the currently used model for system failure times is updated
like in case of a trigger of type (2)
to account for the information gained on components
until the moment of system failure.
Hereafter, a new system is installed,
using the updated models for all components based on the insight obtained from the concluded operational cycle.

At first sight, the above quasi-continous updating of the component failure models,
and the system reliability block diagram,
as well as redetermining the best moment to replace the system,
seems to result in a (very) nervous maintenance policy.
However, due to the very short calculation times,
only at certain moments in time people involved in the execution of maintenance tasks
need to receive detailed information,
whereas during the remaining time,
all can be handled automatically, as done at the moment within, e.g., many safety systems.

The setup of the rest of the paper is as follows.
In Section~\ref{sec:literature}, we show our contribution to the CBM literature.
Next, in Sections~\ref{sec:sysrel}, \ref{sec:adaptive-sysrel-weibull} and \ref{sec:policy},
the three main steps in our policy are discussed in detail.
Hereafter, in Sections~\ref{sec:examples} and \ref{sec:sim},
our policy is applied further to an example.
Finally, in Section~\ref{sec:outlook},
a short summary and our main conclusions are given,
followed by some suggestions for further research.

\iffalse
% ----------------------------------------------------------------------------------------------------
\subsection*{---------------------}
***general discussion on CBM as usual

@@

***In both cases, maintenance decision via control limit / threshold for the signal
(RUL not explicitely calculated)
by minimizing the expected unit cost rate,
which is often approximated using the renewal reward theorem.
%but in practice threshold often not known
\subsection*{---------------------}

@@

***compare to $M^*$ out of $N$ policy:
we are dynamic (would mean for a $M^*$ out of $N$ policy that $M^*$ decreases over time due to component aging),
we learn about component lifetimes,
and we allow for set-up time
\fi
% ----------------------------------------------------------------------------------------------------

\section{Literature review}
\label{sec:literature}
